---
title: "NAME TADA Final Report"
subtitle: "NAME"
author: Ana Benevides, Carol Sobral, Stefania Molina
date: "`r Sys.Date()`" 
output: 
  html_document:
    code_folding: hide 
    toc: yes
    theme: paper
    toc_float:
      collapsed: yes
    df_print: kable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.align = 'center')
```

```{r message=FALSE, warning=FALSE}
library(dplyr)
library(ggplot2)
library(ggrepel)
library(tidyverse)
library(tidytext)
library(quanteda)
library(quanteda.textmodels)
library(austin)
```

# Introduction
<style> body {text-align: justify} </style>

With the support of a Party coalition named “Brazil above everything, God above everyone”, Bolsonaro was elected, in 2018, president of Brazil for the 2019-2022 term. Having served as congress representative (“deputado federal”) for the State of Rio de Janeiro since 1991, Bolsonaro reached notoriety for his populist and often sexist, homophobic, anti-human rights, anti-democratic political views.

After 4 consecutive elections of a left party (“Labour Party”, i.e. “Partido do Trabalhadores” – PT) for the presidency of Brazil, and in the aftermath of a controversial conviction of its most prominent leader -- and front runner in the election polls --  on corruption charges, Bolsonaro benefited from a rise in anti-leftness sentiment and took the leadership of the poll of candidates with a manifesto that was filled with religious/Christian language and that was based on three pillars, that were directly opposed to the agenda of left/progressive groups:
	
1. Liberalization of economic policy: promising deregulation, privatization, and extinction of sectors of the public service;
	
2. Public Security policy: a criminal reform package meant to harden convictions for crimes; exempt law enforcement officials of liability for any deaths they may cause in service; facilitate the private possession of firearms;
	
3. Conservative Moral agenda: opposition of sex education in schools; opposition to policies that aim at extending equality of rights for LGBT people; opposition to pregnancy termination, even in the limited circumstances allowed in Brazilian Law (rape; health risk for the woman; anencephaly of the fetus); reinforcement of gender stereotypical roles.    
	
For this project, we are interested in assessing if, and to what extent, these three axes that constitute Bolsonaro’s political agenda are also resonating in the Brazilian Senate.
	
Brazil’s Senate House is composed of 3 senators per State and the Federal District, totaling 81 senators. Each of their term in office last for 8 years,  but the election cycle happens every 4 years, alternating the elections for 2/3 and 1/3 of the house.  Theoretically speaking, the alternate election cycle should render the Senate house less sensitive to momentary waves that, if salient in a given moment, could heavily influence the course of a presidential election. 
	
In 2018, 2/3 of the Senate chairs were elected (54 senators), while the remaining 1/3 had still half the term in office to complete. 
	
In this project, we analyzed the corpus of Senators’ speeches from the years 2019-2020, focusing on issues associated with these salient dimensions of Bolsonaro’s political plan.


# Data

**WRITE: Describe data sets.**

- `sen_df: 
- `speech_df:
- `cemf_2019:
- `pres_df:

```{r Data_corpus_DFM}
# Senators data frame
load('data/sen_df.Rda')

# Senate speeches data frame
load('data/speech_df.Rda')

# Party position per media outlet - Congresso em Foco 2019
load('data/cemf_2019.Rda') 

# 2018's presidential election manifestos
load('data/pres_df.Rda')
```


# Senate 

## General Characteristics {.tabset}

Considering that the 26 States plus the Federal District each are entitled to three senates, we would expect the sen_df to have 81 senators, however, Roraima (RR) had one of its senators (Chico Rodrigues) suspended from his activities following an investigation on diversion of resources. For this analysis, we will consider the Federal District a state.

The Senate API only displays current senators' speeches, which is why Roraima only has 2 senators and the corpus only comprises speeches from 80 senators.

In what concerns gender, although females are the majority of the Brazilian population (97 males per 100 females), women represent only 1/8 of the composition of the Senate House. 18 States have only male Senators (including Roraima, with only 2 Senators); 8 States have 2 Male Senators and 1 Female Senator and 1 State has 2 Female Senators and 1 Male Senator (Mato Grosso do Sul - MS)

In terms of party distribution, 16 parties have at least one senator in the present term. MDB, PSD, and PODEMOS are the parties with the largest representation, holding 13, 12, and 10 senators, respectively. All of PSD Senators are male, while PSD and PODEMOS have 1 Female Senator each. 

Looking into the distribution of gender per party, 9 of these parties have at least one Female Senator; but only 1 party (PP) has 2 Female Senators.

Considering these characteristics of the Senate House, let's see if the speech distribution follows the same pattern, i.e., let's check if Females' are responsible for 1/8 of the total speeches, and how speeches are distributed among these 16 Parties, and among the 27 states.


### Gender

We see that women represent 12.5% of the Senate but are responsible for only 8.79% of the speeches. This result seems consistent with indicators for gender inequality in Brazil and their effects on women in the workplace.

```{r Gender_Senate, message=FALSE, warning=FALSE}
# Expected frequency of speeches per gender -- based on the number of  senators
expected <-  sen_df %>% 
  group_by(gender) %>% 
  summarise(n = n()) %>% 
  mutate(prop = (n / sum(n))*100) %>% 
  rename(n_sen = n, prop_sen = prop, Gender = gender)

# Observed frequency of speeches
observed <- speech_df  %>% 
  group_by(Gender) %>% 
  summarise(n = n()) %>% 
  mutate(prop = (n / sum(n))*100) %>% 
  rename(n_speech = n, prop_speech = prop)

merge(expected, observed, by = 'Gender') %>% 
  select(Gender, prop_sen, prop_speech) %>% 
  pivot_longer(!Gender, names_to = 'Proportion', values_to = 'Value') %>% 
  mutate(across(is.numeric, ~ round(., 2))) %>% 
  ggplot(aes(Value, Proportion, group = Gender, fill = Gender)) +
  geom_col(position = 'dodge') + 
  geom_text(aes(label = Value), position = position_dodge(0.9), 
            show.legend = FALSE, vjust = -0.5) +
  coord_flip() +
  theme_minimal()
```


### Parties

In what concerns the distribution of speeches per party, we expected MDB, PODEMOS, and PSD to have a higher number of speeches, as they account for a larger percentage of the Senate House. 

```{r Parties_Senate, message=FALSE, warning=FALSE}
# Plot senators by party
party_sen <- sen_df %>% 
  group_by(party_abbr) %>% 
  summarise(n = n()) %>%
  ggplot(aes(party_abbr, n)) +
  geom_col(fill = '#00BFC4') +
  ylab('Number of Senators') +
  xlab('Parties in Senate') +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 90)) 

# Plot speeches by party
party_speech <- speech_df %>% 
  group_by(Partido) %>% 
  summarise(n = n()) %>%
  ggplot(aes(Partido, n)) +
  geom_col(fill = '#F8766D') +
  ylab('Speeches (2019 & 2020)') +
  xlab('Parties in Senate') +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 90))

gridExtra::grid.arrange(party_sen, party_speech)
```

What we find out is that PT, with only 6 Senators (8% of the Senate House) has 1097 speeches (21% of the speeches). PT was the runner-off party of the 2018 elections and was the party elected for the presidential elections of 2002, 2006, 2010, and 2014. This finding might indicate a higher opposition to Bolsonaro's agenda within the Senate corpus.

```{r Prop_Speeches_Party, message=FALSE, warning=FALSE}
# Number of speeches
n_speeches <- speech_df %>% 
  group_by(Partido) %>% 
  summarise(Speeches = n()) %>%
  mutate(Prop_Speeches = round((Speeches / sum(Speeches))*100, 2))

# Number of senators/total
n_senators <- sen_df %>% 
  rename(Partido = 'party_abbr') %>% 
  group_by(Partido) %>% 
  summarise(Senators = n()) %>%
  mutate(Prop_Senators = (Senators / sum(Senators))*100) 


merge(n_speeches, n_senators, by = 'Partido') %>% 
  select(Partido, Prop_Senators, Prop_Speeches) %>% 
  arrange(desc(Prop_Speeches)) %>% 
  mutate(diff = Prop_Speeches - Prop_Senators) %>% 
  group_by(Partido) %>% 
  ggplot(aes(Partido, diff, label = diff, fill = ifelse(diff < 0, '#00BFC4', '#F8766D'))) +
  geom_col() +
  geom_text(aes(y = diff + 2 * sign(diff), label = diff), 
            position = position_dodge(width = 0.9)) +
  ylab('XXXXXXX') +
  xlab('Party') +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 90), legend.position = 'none') 
```

**WRITE**

```{r}
# Party Changes
change <- speech_df %>% 
  group_by(Nome, Partido) %>% 
  count() 

# Create List 
list_change <- change %>% 
  group_by(Nome) %>% 
  count() %>% 
  filter(n > 1) %>% 
  pull(Nome)

# Subset
final_change <- change %>% 
  subset(Nome %in% list_change) %>% 
  select(Nome, Partido)

# Print
final_change
```


### States

Our data set is composed of 5188 speeches given by 80 Senators of 27 States. Assuming each Senator uses speech opportunities equally, we would expect each State to have around 192 speeches. Let's see if this checks out.

What we see is that Senators coming from some States, such as RS, PE, DF, and AP far exceed the expected average of speeches; at the same time, Senators from PB, AC, and RJ seem not to have spoken as much as their peers in 2019 and 2020. 

This might indicate that the items relevant for the agenda of the States that have more speeches might bear higher weight in the corpus.

```{r UF_Senate, message=FALSE, warning=FALSE}
state_sen <- sen_df %>% 
  group_by(state) %>% 
  summarise(n = n()) %>%
  ggplot(aes(state, n)) +
  geom_col(fill = '#00BFC4') +
  ylab('Senators per State') +
  xlab('States of Brazil') +
  theme_classic()  

# Plot speeches by state
state_speech <- speech_df %>% 
  group_by(UfParlamentarNaData) %>% 
  summarise(n = n()) %>%
  ggplot(aes(UfParlamentarNaData, n)) +
  geom_col(fill = '#F8766D') +
  geom_hline(yintercept = 192, linetype = 'dotted', col = 'blue') +
  ylab('Speeches (2019 & 2020)') +
  xlab('States of Brazil') +
  theme_classic() 

gridExtra::grid.arrange(state_sen, state_speech)
```


## Speeches Scaling 

First, we use Wordfish as the text scaling method for the Senate speeches. After, as shown below, we plot the results of a fitted scaling model. 

**WRITE: descrição do gráfico.**

```{r RILE_speaches}
# Main Senate Corpus 
corp_sen <- corpus(speech_df, docid_field = 'CodigoPronunciamento', 
                   text_field = 'Pronunciamento')

# Main Senate DFM
dfmat_sen <- dfm(corp_sen,
  tolower = TRUE,
  remove_punct = TRUE,
  remove = stopwords('portuguese'),
  remove_numbers = TRUE,
  remove_separators = TRUE,
  remove_symbols = TRUE,
  stem = FALSE,  
  groups = 'Partido')

dfmat_sen <- dfm_select(dfmat_sen, min_nchar = 2)
docnames(dfmat_sen) <- paste(dfmat_sen$Partido)

# Wordfish
wf <- textmodel_wordfish(dfmat_sen, dir = c(16, 6), sparse = TRUE) # PT and PL
textplot_scale1d(wf)
```

### Wordfish Scores X Media {.tabset}

To better understand the Senate speeches position generated with Wordfish, we compare it with media perception of each party. 


#### NAME Main Graph 

The graph below shows the *Congresso em Foco* (y-axis) and the Wordfish categorization (x-axis) for each party. 

Some parties appear as similar positions in both situations, such as PSB, PSDB, and MDB. On the other hand, the Wordfish model considers PT on the extreme left, around -2 on the scale. In contrast, the Media considers the same party on the left, around -1 on the scale.

We see the same pattern on the other side of the scale. While the Media considers PSL on the right, the Wordfish model assumes the same party in the center position.  

```{r RILE_media, message=FALSE, warning=FALSE}
# Code right, left, center positions 
cemf_2019 <-  cemf_2019 %>% 
  mutate(score = if_else(pos == 'centro', 0, if_else(pos == 'esquerda', -1, 1)))

# Data frame with Wordsfish party positions from Senate Speeches
theta_sen_wf <- as.data.frame(wf$theta, wf$docs) %>% 
    rownames_to_column('party') %>%
    rename(theta_sen_wf = 'wf$theta')

# Merge
scores <- merge(theta_sen_wf, cemf_2019, by = 'party') 

scores %>% 
  arrange(score) %>%    
  mutate(party = factor(party, levels = party)) %>% 
  ggplot(aes(x = theta_sen_wf, y = score, label = party, col = party)) + 
  geom_point() + 
  geom_label_repel(show.legend = FALSE) +
  geom_abline(linetype = 'dotted') +
  xlim(-2.5, 3) +
  ylim(-2.5, 3) +
  ylab('Media Position') +
  xlab('Wordfish Position') +
  theme_minimal() +
  theme(legend.position = 'none') 
```

#### NAME Ana

**WRITE**

```{r message=FALSE, warning=FALSE}
# Media and number of senators
sen_df %>% 
  group_by(party_abbr) %>% 
  summarise(n = n()) %>% 
  rename(party = 'party_abbr') %>% 
  merge(scores, by = 'party') %>%  
  arrange(score) %>%    
  mutate(party = factor(party, levels = party)) %>% 
  ggplot(aes(x = theta_sen_wf, y = score, size = n, color = party)) + 
  geom_point() + 
  geom_label_repel(aes(label = party), size = 3) +
  scale_size_area(max_size = 16) +
  geom_abline(linetype = 'dotted') +
  xlim(-2.5, 3) +
  ylim(-2.5, 3) +
  ylab('Media Position') +
  xlab('Wordfish Position') +
  theme_minimal() +
  theme(legend.position = 'none') 
```

#### NAME Ana

**WRITE**

```{r message=FALSE, warning=FALSE}
# Media and number of speeches
speech_df %>% 
  group_by(Partido) %>% 
  summarise(n = n()) %>% 
  rename(party = 'Partido') %>% 
  merge(scores, by = 'party') %>%  
  arrange(score) %>%    
  mutate(party = factor(party, levels = party)) %>% 
  ggplot(aes(x = theta_sen_wf, y = score, size = n, color = party)) + 
  geom_point() + 
  geom_label_repel(aes(label = party), size = 3) +
  scale_size_area(max_size = 16) +
  geom_abline(linetype = 'dotted') +
  xlim(-2.5, 3) +
  ylim(-2.5, 3) +
  ylab('Media Position') +
  xlab('Wordfish Position') +
  theme_minimal() +
  theme(legend.position = 'none')
```


### 2018's Presidential Manifestos {.tabset}

In this section, we compare Senate speeches position generated with Wordfish with presidential manifestos from 2018. 

```{r Presidential_Campaign}
# Corpus Presidential Speeches
corp_pres <- corpus(pres_df, docid_field = 'party', 
                   text_field = 'text')

# DFM 
dfmat_pres <- dfm(corp_pres,
  tolower = TRUE,
  remove_punct = TRUE,
  remove = stopwords('portuguese'),
  remove_numbers = TRUE,
  remove_separators = TRUE,
  remove_symbols = TRUE,
  stem = FALSE)

dfmat_pres <- dfm_select(dfmat_pres, min_nchar = 2)
```


#### NAME only in pres election

The graph illustrates party positions derived from the Presidential manifestos (Y-axis) and the Senate speeches (X-axis) using `wordfish` prediction. 

It is possible to see a pattern where parties are mostly allocated to the right when using Senate speeches. Although, when analyzing Presidential manifestos, parties are mostly located to the left. There is one exception of PDT, which is around the center spectrum on Presidential corpus, and on the extreme left for the Senate corpus. 

```{r message=FALSE, warning=FALSE}
# Austin
# Convert to WFM
wfm_pres <- as.wfm(dfmat_pres, word.margin = 2)

# Wordfish pres
wfa_pres <- wordfish(wfm_pres, dir = c(4, 3)) # PSOL, PSL

# pres scores
theta_pres_au <- as.data.frame(wfa_pres$theta, wfa_pres$docs) %>%
  rownames_to_column('party') %>%
  rename(theta_pres = 'wfa_pres$theta')

# Match sen features with pres
dfmat_sen_match <- dfm_match(dfmat_sen, featnames(dfmat_pres))

# Convert to WFM
wfm_sen <- as.wfm(dfmat_sen_match, word.margin = 2)

# Out of sample Austin prediction to senate speeches
theta_sen_au <- as.data.frame(predict(wfa_pres, newdata = wfm_sen)) %>%
  rownames_to_column('party') %>%
  rename(theta_sen_au = 'predict(wfa_pres, newdata = wfm_sen)')

# merge dfs -- theta pres and sen
theta_ps <- merge(theta_pres_au, theta_sen_au, by = 'party')

# Compare pres x sen
theta_ps %>% 
  arrange(theta_pres) %>%    
  mutate(party = factor(party, levels = party)) %>% 
  ggplot(aes(x = theta_pres, y = theta_sen_au, label = party, col = party)) + 
  geom_point() + 
  geom_label_repel(show.legend = FALSE) +
  geom_abline(linetype = 'dotted') +
  xlim(-2, 2) +
  ylim(-2, 2) +
  ylab('Position from Presidential Corpus') +
  xlab('Position from Senate Corpus') +
  theme_minimal() +
  theme(legend.position = 'none') 
```


#### NAME all parties in senate

The graph shows the party positions derived from the Presidential manifestos (Y-axis) using `austin` prediction and the Senate speeches (X-axis) using `wordfish` prediction. 

We see that `austin` predictions are more centered, while `wordfish` is more polarized. For example, PL is on the center spectrum for the first and the extreme right for the second.

```{r}
# Compare wf_sen x out of sample Austin prediction to senate speeches
merge(theta_sen_wf, theta_sen_au, by = 'party') %>% 
  arrange(theta_sen_wf) %>%    
  mutate(party = factor(party, levels = party)) %>% 
  ggplot(aes(x = theta_sen_wf, y = theta_sen_au, label = party, col = party)) + 
  geom_point() + 
  geom_label_repel(show.legend = FALSE) +
  geom_abline(linetype = 'dotted') +
  xlim(-3, 3) +
  ylim(-3, 3) +
  ylab('Position from Presidential Corpus') +
  xlab('Position from Senate Corpus') +
  theme_minimal() +
  theme(legend.position = 'none') 
```


# Themes

Having assessed how the parties in the senate are positioned in the RILE Scale, let's check how the discussions on the three topics of Bolsonaro's agenda appear in the Senate House. 

For this section, we employed a dictionary analysis, identifying a few words with each topic to classify the corpus accordingly.

We initially consulted the  “LexiCoder Policy Agenda” dictionary to have a baseline for words that could capture these main topics. We then translated the words into Portuguese and adapted them for the Brazilian context. 

In the following sections, we will analyze the three aforementioned dimensions under the topics Economy, Security, and Gender & Family. 

```{r}
# Create Dictionary with themes of interest
theme.lexicon <- dictionary(list(economy = c('econom*', 'desempreg*', 'inflação', 'demanda', 'oferta', 'negócios', 'empreg*', 'preço*', 'banco', 'dinheiro', 'gastos', 'dívida', 'juro*', 'control*', 'custo*', 'produtividade', 'índice', 'renda', 'pib', 'produto', 'bruto', 'empreg*', 'trabalh*', 'privat*', 'auxílio', 'desigualdade', 'petróleo', 'petro', 'desigual*', 'custo*', 'capital', 'ações', 'participação', 'aposent*', 'nacionalizar', 'mercado'), genfam = c('famíl*', 'famil*', 'just*', 'mulher*', 'solteir*', 'sex*', 'pai*', 'mãe', 'filh*', 'abort*', 'criança*', 'abrigo', 'gênero', 'gay', 'kit gay', 'jove*', 'juventude', 'tradicional'), security = c('sequestr*', 'inocent*', 'puni*','condena*','sentença', 'tribunal', 'juiz', 'justiça', 'crim*', 'bandid*', 'criminos*', 'ilícit*', 'infrator*', 'impunidade', 'promotor*', 'instância', 'transitado', 'julgado', 'julgamento', 'bala', 'balead*', 'tiro', 'fuzil', 'arma', 'armamento', 'pistola', 'rifle', 'polícia', 'policial', 'militar', 'cidadão de bem', 'cadeia*', 'prisão', 'prisioneir*', 'investigação', 'intervenção militar', 'UPP', 'segurança pública', '*anticrime', '*anti-crime', 'assassin*', 'ladrão', 'vagabund*', 'saidão', 'condicional', 'progressão de regime', 'réu', 'defensoria', 'estupr*', 'traficante*', 'detenção', 'detent*',  'violência', 'reinci*', 'delinquente', 'menor', 'maioridade penal', 'drogas', 'entorpecent*')))

# Create DFM with theme.lexicon, apply weights and convert to data frame
theme_df  <- dfm(corp_sen, dictionary = theme.lexicon) %>% 
    dfm_weight(scheme = 'prop') %>% 
    convert('data.frame')
```


## Economy {.tabset}

To extract documents that discuss economic topics, we filtered documents that have higher scores on the economy dictionary when compared to the security and gender & family dictionaries. 

```{r}
# List with documents about economy
econ_id <- theme_df %>% 
  filter(economy > genfam & economy > security) %>% 
  pull(doc_id)

# DFM with econ documents
dfmat_econ <- speech_df %>% 
  subset(CodigoPronunciamento %in% econ_id) %>% 
  corpus(docid_field = 'CodigoPronunciamento', text_field = 'Pronunciamento') %>% 
  dfm(tolower = TRUE,
      remove_punct = TRUE,
      remove = stopwords('portuguese'),
      remove_numbers = TRUE,
      remove_separators = TRUE,
      remove_symbols = TRUE,
      stem = FALSE,  
      groups = 'Partido')

dfmat_econ <- dfm_select(dfmat_econ, min_nchar = 2)
```

### Scaling

Comparing the economy graph for Wordfish with the main graph, we do not see much difference in party positions. This might suggest that discussions on the Economy are the main driver behind the allocation of parties in the RILE spectrum. In other words, views on economic matters could bear a high weight in the definition of where a party is positioned in the ideological spectrum. This suggests that economic discussions are more salient in the corpus. 

```{r}
# Wordfish for economy DFM
wf_econ <- textmodel_wordfish(dfmat_econ, dir = c(16, 6), sparse = TRUE) # PT and PR


# Plot economy and main DFM graphs
gridExtra::grid.arrange(textplot_scale1d(wf_econ), textplot_scale1d(wf), ncol = 2, 
                        bottom = 'Economy DFM --- Main DFM')
```

### RILE Features

The graph displays words that push a document farthest to the left or the right. Words located at the bottom are used less frequently. Right and left word positions (beta) range from approximately -2.5 to 2. 

The words that most contributed for a left-leaning document are *petrobrás (an oil extracting public company whose privatization is a contentious topic), anticapitalista ('anticapitalist'), cut ('centralized labour union'),  auxílio-doença ('illness aid',an employment benefit), sindicalista* ('unionist') and *terceirização* ('outsourcing'). 

For the right, the words are *militarismo ('militarism'), agroindustriais ('agribusiness'), grevista ('striker'), veterinária ('veterinarian'), logística* ('logistics') and *transportes* ('transport'). 

In general, the right discusses business, agriculture, and themes related to a somewhat liberal agenda (with words like entrepreneurship, liberalism, and infrastructure). The left discusses pension benefits, worker's rights, and trade unionism. 

Both sides talk about macroeconomic policies, with words like inflation, GDP, debt, and spending.

```{r}
# Features usage left/right
feat_econ <- data.frame(
  word = wf_econ$features,
  beta = wf_econ$beta,
  psi = wf_econ$psi,
  stringsAsFactors = FALSE)

# Select words for graph
words_econ <- c('trabalhadores', 'direitos', 'aposentados', 'pensionistas', 'escrvavidão', 'liberal',
                'petrobrás', 'auxílio', 'previdência', 'covid', 'desempregado', 'sindical', 
                'amazônia', 'terceirização', 'agroindustriais', 'militarismo', 'grevista','emprego',
                'veterinária', 'agropecuárias', 'pib', 'dívida', 'impostos', 'gastos', 'minerador',
                'concessões', 'logística', 'transportes', 'obra', 'anticapitalista','inflação',
                'infraestrutura', 'pobres', 'reforma', 'agricultura', 'auxílio-doença',
                'sindicalista', 'cut', 'reindustrialização','simplificar', 'empreendedorismo')

# Extract scores
scores_econ <- arrange(filter(feat_econ, word %in% words_econ), beta)

# Plot words on the RILE scale
ggplot(scores_econ, aes(beta, psi, label = word)) +
  geom_point(data = scores_econ, color = ifelse(scores_econ$beta > 0, '#00BFC4', '#F8766D')) +
  geom_text_repel(data = scores_econ, col = 'black') +
  labs(x = 'Word Score', y = 'Word Frequency') +
  ggtitle('Estimated Word Positions for Economy Vocabulary') +
  geom_vline(xintercept = c(0,0), linetype = 'dotted') +
  theme_minimal()
```


## Security {.tabset}

To extract documents that discuss security topics, we filtered documents that have higher scores on the security dictionary when compared to the economy and gender & family dictionaries.

```{r Security_analysis}
# List with documents about security
sec_id <- theme_df %>% 
  filter(security > genfam & security > economy) %>% 
  pull(doc_id)

# DFM with sec documents
dfmat_sec <- speech_df %>% 
  subset(CodigoPronunciamento %in% sec_id) %>% 
  corpus(docid_field = 'CodigoPronunciamento', text_field = 'Pronunciamento') %>% 
  dfm(tolower = TRUE,
      remove_punct = TRUE,
      remove = stopwords('portuguese'),
      remove_numbers = TRUE,
      remove_separators = TRUE,
      remove_symbols = TRUE,
      stem = FALSE,  
      groups = 'Partido')

dfmat_sec <- dfm_select(dfmat_sec, min_nchar = 2)
```

### Scaling

see a lot of change in party positions. This may suggest that security bears a smaller weight into defining general parties' positions, and/or there is a lot of overlap in the security vocabulary used by senators across the spectrum.

```{r}
# Wordfish for security DFM
wf_sec <- textmodel_wordfish(dfmat_sec, dir = c(16, 6), sparse = TRUE) # PT and PL

# Plot security and main DFM graphs
gridExtra::grid.arrange(textplot_scale1d(wf_sec), textplot_scale1d(wf), ncol = 2, 
                        bottom = 'Security DFM --- Main DFM')
```

### RILE Features

The graph displays words that push a document farthest to the left or the right. Words located at the bottom are used less frequently. Right and left word positions range from approximately -1.5 to 1.5.

The words that most contributed for a left-leaning document are defensoria ('public attorney office'), defensores ('public attorneys'), direitos ('rights'), humanos ('human'), perseguição ('harassment'), liberdade ('freedom') . For the right, the words are vagabundo(s) ('tramps'), juvenis ('juvenile'), tropa ('troop'), pcc (the largest gang in SP), farda ('police suit').

In general, the right discusses crime, criminals, and law enforcement activities, while the left discusses human rights and judicial harassment.

Interestingly, the use of cadeia ('jail') and prisão ('prison'), which are synonyms in Portuguese, seems associated with speeches on different sides of the RILE spectrum. Similarly, the word vagabundagem (idleness that characterizes a tramp) and vagabundo (s) ('tramp') are also associated with different sides of RILE.

Finally, 'feminicídio' (a relatively new criminal offense for an aggravated homicide committed against a woman by her former romantic partner), which is a differentiation to standard homicide typically criticized by right-wing politicians with a conservative view of gender issues, is the word that appears most strongly associated with a right-leaning political view.

```{r}
# Features usage left/right
feat_sec <- data.frame(
  word = wf_sec$features,
  beta = wf_sec$beta,
  psi = wf_sec$psi,
  stringsAsFactors = FALSE)

# Select words for graph
words_sec <- c('bandidagem','direitos', 'humanos','juiz','perseguição', 'liberdade', 
               'defesa','violência','cadeia', 'prisão', 'vagabundo', 'vagabundos', 'vagabundagem', 
               'juvenis','arma', 'tiro', 'feminicídio', 'fiança','militar')
              
# Extract scores
scores_sec <- arrange(filter(feat_sec, word %in% words_sec), beta)

# Plot words on the RILE scale
ggplot(scores_sec, aes(beta, psi, label = word)) +
  geom_point(color = ifelse(scores_sec$beta > 0, '#00BFC4', '#F8766D')) +
  geom_text_repel(data = scores_sec, col = 'black') +
  labs(x = 'Word Score', y = 'Word Frequency') +
  ggtitle('Estimated Word Positions for Security Vocabulary') + 
  geom_vline(xintercept = c(0,0), linetype = 'dotted') +
  theme_minimal()
```

## Gender & Family {.tabset}

To extract documents that discuss Gender and Family topics, we filter documents that have higher scores on the genfam dictionary when compared to the economy and security dictionaries. 

```{r}
# List with documents about gender and family 
genfam_id <- theme_df %>% 
  filter(genfam > security & genfam > economy) %>% 
  pull(doc_id)

# DFM with genfam documents
dfmat_genfam <- speech_df %>% 
  subset(CodigoPronunciamento %in% genfam_id) %>% 
  corpus(docid_field = 'CodigoPronunciamento', text_field = 'Pronunciamento') %>% 
  dfm(tolower = TRUE,
      remove_punct = TRUE,
      remove = stopwords('portuguese'),
      remove_numbers = TRUE,
      remove_separators = TRUE,
      remove_symbols = TRUE,
      stem = FALSE,  
      groups = 'Partido')

dfmat_genfam <- dfm_trim(dfmat_genfam, min_termfreq = 2, min_docfreq = 2)
```

### Scaling

Comparing the gender and family graph for Wordfish with the main graph, we see some change in party positions. The party PT is considered extreme left on the main DFM, while left on the genfam DFM. Topics included in gender and family might not be one of the main drivers behind the allocation of parties in the RILE spectrum. Furthermore, this suggests that genfam bears a smaller weight into defining general parties' positions, and/or there is a lot of overlap in the genfam vocabulary used by senators across the spectrum.

```{r}
# Wordfish for gender and family DFM
wf_genfam <- textmodel_wordfish(dfmat_genfam, dir = c(16, 6), sparse = TRUE) # PT and PL

# Plot gender & family and main DFM graphs
gridExtra::grid.arrange(textplot_scale1d(wf_genfam), textplot_scale1d(wf), ncol = 2, 
                        bottom = 'Gender & Family DFM --- Main DFM')
```

### RILE Features

The graph displays words that push a document farthest to the left or the right. Words located at the bottom are used less frequently. Right and left word positions range from approximately -0.5 to 0.5.

The word that most contributes to a left-leaning document is resistência ('resistance'). The words that most contribute to a right-leaning document are tradicional ('traditional') and esposa ('wife'). All the other words are close to the center. 

Finally, words that we expected to be highly significant don't even appear in speeches. Some examples are sexista ('sexist') and 'gay'.

```{r}
# Features usage left/right
feat_genfam <- data.frame(
  word = wf_genfam$features,
  beta = wf_genfam$beta,
  psi = wf_genfam$psi,
  stringsAsFactors = FALSE)

# Select words for graph
words_genfam <- c('tradicional', 'mulher', 'gênero', 'sexo', 'homem', 'feminista', 'juventude', 
                  'jovem', 'jovens', 'família', 'resistência', 'direito', 'crianças', 'mãe', 'mães', 
                  'pai', 'justiça', 'feminina', 'marido', 'esposa', 'casal')

#Extract scores
scores_genfam <- arrange(filter(feat_genfam, word %in% words_genfam), beta)

# Plot words on the RILE scale 
ggplot(scores_genfam, aes(beta, psi, label = word)) +
  geom_point(color = ifelse(scores_genfam$beta > 0, '#00BFC4', '#F8766D')) +
  geom_text_repel(data = scores_genfam, col = 'black') +
  labs(x = 'Word Score', y = 'Word Frequency') +
  ggtitle('Estimated Word Positions for Gender and Family Vocabulary') + geom_vline(xintercept = 
          c(0,0), linetype = 'dotted') +
  theme_minimal()
```


# Conclusion 

From the analyses made in this project, we understand that it is not all the views present in the populist discourse of President Jair Bolsonaro that are also present in the speeches of the Brazilian Senate.

The themes and famous phrases mentioned by the current President, which are mostly propagated by the Media, are not present in the same intensity in the Senate environment. On the other hand, this might be related to the percentage of representation of each party in the Senate. Take PT as an example; it is one of the main opposition parties to Bolsonaro and has a large Senate representation. Thus, most of their speeches are against what is defended by the President. 

When analyzing the three main themes highlighted in Bolsonaro’s campaign, the economy is the most present in the Senate. In comparison, security and gender & family appear less frequently, respectively.