---
title: 'Brazilian Senate Speeches'
output: 
  html_document: 
    toc: yes
    theme: paper
    toc_float:
      collapsed: no
    df_print: kable
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r message=FALSE, warning=FALSE}
library(dplyr)
library(ggrepel)
library(ggplot2)
library(tidyverse)
library(tidytext)
library(quanteda)
library(quanteda.textmodels)
library(stm)
```

# Ideas

* Plot wordfish scores x perceived party position by media -- `wiki_partidos`.
* Scale speeches separated by theme (economy, 'societal policy', [...]) -- separation by dictionaries? topic modeling?
  * Display top 'left' and 'right' words in a bar plot. 


# Data

```{r}
# Load senators data frame
load('data/sen_df.Rda')
glimpse(sen_df)

# Load speeches data frame
load('data/speech_df.Rda')
glimpse(speech_df)
```


```{r}
# Corpus
corp_sen <- corpus(speech_df, docid_field = 'CodigoPronunciamento', 
                     text_field = 'Pronunciamento')

# DFM
dfmat_sen <- dfm(corp_sen,
  tolower = TRUE,
  remove_punct = TRUE,
  remove = stopwords('portuguese'),
  remove_numbers = TRUE,
  remove_separators = TRUE,
  remove_symbols = TRUE,
  stem = FALSE,  
  groups = 'Partido')


# Additional stopwords
stopwords1 <- c('presidente', 'exa', 'excelencia', 'senhor', 'aqui', 'porque', 'ser',
                'então', 'quero', 'vai', 'ainda', 'ter', 'pode', 'bem', 'obrigado',
                'assim', 'dessa', 'srs', 'cada', 'portanto', 'outro', 'toda', 'além', 
                'nesse', 'nesta', 'desta', 'deste', 'disso', 'sra', 'pois', 'nó', 'sr',
                'aí', 'senador', 'senadores')


# Remove additional stopwords
dfmat_sen <- dfm_remove(dfmat_sen, stopwords1)

# Set minumum number of characters
dfmat_sen <- dfm_select(dfmat_sen, min_nchar = 2)

# Keep only words occurring in at most 9/10 of the documents
## acho que não precisa já que a análise vai ser de palavras usadas pelos dois lados. + se usarmos essa função, a palavra 'deus' sai da dfm. ##
#dfmat_sen <- dfm_trim(dfmat_sen, max_docfreq = 0.95, docfreq_type = 'prop')

# Name documents
docnames(dfmat_sen) <- paste(dfmat_sen$Partido)

# Summary 
head(dfm_sort(dfmat_sen, decreasing = TRUE, margin = 'both'), n = 10, nf = 5) 
```


# Number of senators/speeches

## By Gender

```{r message=FALSE, warning=FALSE}
# Table
sen_df %>% 
  group_by(party_abbr, gender) %>% 
  summarise(n = n()) %>% 
  ungroup() %>% 
  mutate(prop = (n / sum(n))*100) %>% 
  DT::datatable()


# Plot senators by gender
gender_sen <- sen_df %>% 
  group_by(party_abbr, gender) %>% 
  summarise(n = n()) %>%
  ggplot(aes(party_abbr, n)) +
  geom_col(aes(fill = gender)) +
  ylab('# Senators') +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 90)) 

# Plot speeches by gender
gender_speech <- speech_df %>% 
  group_by(Partido, Gender) %>% 
  summarise(n = n()) %>%
  ggplot(aes(Partido, n)) +
  geom_col(aes(fill = Gender)) +
  ylab('# Speeches') +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 90))

gridExtra::grid.arrange(gender_sen, gender_speech)
```


## By State
```{r message=FALSE, warning=FALSE}
# Plot senators by state
# https://www25.senado.leg.br/web/senadores/por-uf/-/uf/RR -- RR 2 senadores
state_sen <- sen_df %>% 
  group_by(state, gender) %>% 
  summarise(n = n()) %>%
  ggplot(aes(state, n)) +
  geom_col(aes(fill = gender)) +
  ylab('# Senators') +
  theme_classic() 

# Plot speeches by state
state_speech <- speech_df %>% 
  group_by(UfParlamentarNaData, Gender) %>% 
  summarise(n = n()) %>%
  ggplot(aes(UfParlamentarNaData, n)) +
  geom_col(aes(fill = Gender)) +
  ylab('# Speeches') +
  theme_classic() 

gridExtra::grid.arrange(state_sen, state_speech)
```


# Keyness 

```{r}
textplot_keyness(textstat_keyness(dfmat_sen, target = dfmat_sen$Partido == 'PSL'))
textplot_keyness(textstat_keyness(dfmat_sen, target = dfmat_sen$Partido == 'PT'))
textplot_keyness(textstat_keyness(dfmat_sen, target = dfmat_sen$Partido == 'PSDB'))
```


# Wordfish

```{r}
# Print doc 20
dfmat_sen[20, 1] # PT

# Print doc 11
dfmat_sen[11, 1] # PR

# Wordfish model
wf <- textmodel_wordfish(dfmat_sen, dir = c(20, 11), sparse = TRUE)
```

## Party Position

```{r}
# Graph party positions
textplot_scale1d(wf)
```

```{r}
# Table with party position from external sources
load('../tada/data/wiki_partidos.Rda')
wiki_partidos %>% 
  DT::datatable()
```


## Feature Analysis

```{r}
# Features usage left/right
feat <- data.frame(
  word = wf$features,
  beta = wf$beta,
  psi = wf$psi,
  stringsAsFactors = FALSE)


# Graph top 30 psi per beta
# word fixed effects -- capture the fact that some words are used much more often than other words by all actors
feat %>% 
  top_n(30, psi) %>%  
  ggplot(aes(x = beta, y = psi, label = word)) +
  geom_point() +
  geom_text_repel() +
  theme_classic()

# Left
feat_t <- feat %>% 
  top_n(-20, beta)
  #DT::datatable()

# Right
feat_r <- feat %>% 
  top_n(20, beta) 
  #DT::datatable()

rbind(feat_t, feat_r) %>% 
  arrange(beta) %>%    
  mutate(word = factor(word, levels = word)) %>% 
  ggplot(aes(x = word, y = beta)) +
  geom_col() +
  coord_flip() +
  theme_classic()
```


# Topics

## Economy

### Dictionary Analysis

```{r}
# Create Dictionary
# -- economy words from policy_agendas_english --
policy.lexicon <- dictionary(file = 'data/policy_agendas_english.lcd')

theme.lexicon <- dictionary(list(economy = c('econom*', 'desempreg*', 'inflação', 'demanda', 'oferta', 'negócios', 'empreg*', 'preço*', 'banco', 'dinheiro', 'gastos', 'dívida', 'juro*', 'control*', 'custo*', 'produtividade', 'índice', 'renda', 'pib', 'produto', 'bruto', 'empreg*', 'trabalh*', 'privat*'), social = c('mulher*', 'home*', 'famíl*', 'famil*', 'sex*')))


# Create DFM with theme.lexicon, apply weights and convert to data frame
theme_df  <- dfm(corp_sen, dictionary = theme.lexicon) %>% 
    dfm_weight(scheme = 'prop') %>% 
    convert('data.frame')
```


```{r}
# List with documents about economy
econ_id <- theme_df %>% 
  filter(economy > 0.9) %>% 
  pull(doc_id)

# DFM with econ documents
dfmat_econ <- speech_df %>% 
  subset(CodigoPronunciamento %in% econ_id) %>% 
  corpus(docid_field = 'CodigoPronunciamento', text_field = 'Pronunciamento') %>% 
  dfm(tolower = TRUE,
      remove_punct = TRUE,
      remove = stopwords('portuguese'),
      remove_numbers = TRUE,
      remove_separators = TRUE,
      remove_symbols = TRUE,
      stem = FALSE,  
      groups = 'Partido')

# Wordfish for econ
dfmat_econ[20, 1]
dfmat_econ[11, 1]

wf_econ <- textmodel_wordfish(dfmat_econ, dir = c(20, 11), sparse = TRUE)

textplot_scale1d(wf_econ)
```
```{r}
# Features usage left/right
feat_econ <- data.frame(
  word = wf_econ$features,
  beta = wf_econ$beta,
  psi = wf_econ$psi,
  stringsAsFactors = FALSE)


# Graph top 30 psi per beta
feat_econ %>% 
  top_n(30, psi) %>%  # word fixed-effects
  ggplot(aes(x = beta, y = psi, label = word)) +
  geom_point() +
  geom_text_repel() +
  theme_classic()

# Left
econ_t <- feat_econ %>% 
  top_n(-20, beta)
  #DT::datatable()

# Right
econ_r <- feat_econ %>% 
  top_n(20, beta) 
  #DT::datatable()

rbind(econ_t, econ_r) %>% 
  arrange(beta) %>%    
  mutate(word = factor(word, levels = word)) %>% 
  ggplot(aes(x = word, y = beta)) +
  geom_col() +
  coord_flip() +
  theme_classic()

# Graph word positions
#textplot_scale1d(wf_econ, margin = 'features', highlighted = 'petrobrás')
```
```{r}
textplot_keyness(textstat_keyness(dfmat_econ, target = dfmat_sen$Partido == 'PR'))
```

## Social -- só para demonstração

```{r}
# List with documents about social
social_id <- theme_df %>% 
  filter(social > 0.8) %>% 
  pull(doc_id)

# DFM with social documents
dfmat_social <- speech_df %>% 
  subset(CodigoPronunciamento %in% social_id) %>% 
  corpus(docid_field = 'CodigoPronunciamento', text_field = 'Pronunciamento') %>% 
  dfm(tolower = TRUE,
      remove_punct = TRUE,
      remove = stopwords('portuguese'),
      remove_numbers = TRUE,
      remove_separators = TRUE,
      remove_symbols = TRUE,
      stem = FALSE,  
      groups = 'Partido')

# Wordfish for econ
dfmat_social[18, 1]
dfmat_social[11, 1]
wf_social <- textmodel_wordfish(dfmat_social, dir = c(18, 11), sparse = TRUE)
textplot_scale1d(wf_social)
```


## Religion

### Word Collocations

```{r}
# Keyword in context == 'evangélico'
kwic(corp_sen, pattern = 'evangélico', window = 3, valuetype = 'glob')
```


### Word Correlations

```{r message=FALSE, warning=FALSE}
# Convert dfm into relative frequency and find correlations
dfm_weight(dfmat_sen, scheme = 'prop') %>% 
    textstat_simil(selection = c('deus', 'evangélico', 'igreja'), 
                   method = 'correlation', margin = 'features') %>%
    as.matrix() %>%
    head(15)
```


